\item Hadland, N., {\bf Sankar, R.}, LeBeau, R. P., Palotai, C. EPIC simulations of Neptune's dark spots using an active cloud microphysical model. {\it Monthly Notices of the Royal Astronomical Society}. {\it 496}, 4760-4768. (2020)
\item {\bf Sankar, R.}, Palotai, C., Hueso, R., Delcroix, M., Chappel, E., S\'{a}nchez-Lavega, A. Fragmentation modelling of the 2019 August impact on Jupiter. {\it Monthly Notices of the Royal Astronomical Society}. {\it 493}, 4622-4630. (2020)
\item LeBeau, R., Farmer, K., {\bf Sankar, R.}, Hadland, N., Palotai, C. A Numerical Investigation of the Berg Feature on Uranus as a Vortex-Driven System. {\it Atmosphere}. {\it 11}, 52. (2020)
\item Palotai, C., {\bf Sankar, R.}, Free, D. L., Howell, J. A., Botella, E., Batcheldor, D. Analysis of the 2016 June 2 bolide event over Arizona. {\it Monthly Notices of the Royal Astronomical Society}. {\it 487}, 2307-2318. (2019)
\item {\bf Sankar, R.}, Klare, C., Palotai, C. Moist convection in Jupiter's fastest jet. {\it Europlanet Science Congress 2020, online, 21 September–9 Oct 2020}. (2020)
\item {\bf Sankar, R.}, Klare, C., Palotai, C., Hughes, A. Simulation of Jovian moist convection with an active water and ammonia hydrological cycle using the EPIC GCM. {\it AGU Fall Meeting Abstracts}. (2019)
\item Hadland, N., {\bf Sankar, R.}, Klare, C., Palotai, C., Farmer, K., Lebeau, R. EPIC Modeling of Large Scale Dynamical Features of the Gas Giants. {\it EPSC-DPS Joint Meeting 2019}. (2019)
\item Le Beau, R. P., Loiacono, R., Wagner, A., Farmer, K., Palotai, C. J., {\bf Sankar, R.}, Hadland, N., Nodolski, N. Using Numerical Simulation to Consider the Observed Variations in the Behavior and Appearance of Dark Spots on the Ice Giants. {\it American Astronomical Society Meeting Abstracts \#234}. (2019)
\item LeBeau, R., Farmer, K., Palotai, C., Hadland, N., {\bf Sankar, R.}, Nodolski, N. Simulating the Uranian Berg Feature as a Vortex-Driven Cloud. {\it AGU Fall Meeting Abstracts}. (2018)
\item {\bf Sankar, R.}, Hadland, N., Klare, C., Flom, A., Nodolski, N., Palotai, C., LeBeau, R., Farmer, K. Simulations of large scale cloud features on Outer Solar System planets. {\it AAS/Division for Planetary Sciences Meeting Abstracts \#50}. (2018)
\item Le Beau, R. P., Farmer, K., Palotai, C., Hadland, N., {\bf Sankar, R.}, Nodolski, N. Simulating Drifting Features in the Atmospheres of the Ice Giants. {\it AAS/Division for Planetary Sciences Meeting Abstracts \#50}. (2018)
\item LeBeau, R., Koutas, N., Palotai, C., Bhure, S., Hadland, N., {\bf Sankar, R.} Catching the Drift: Simulating Dark Spots and Bright Companions on the Ice Giants. {\it AGU Fall Meeting Abstracts}. (2017)
\item {\bf Sankar, R.}, Palotai, C. J. Analysis of cloud microphysical processes on extrasolar giant planet atmospheres. {\it AAS/Division for Planetary Sciences Meeting Abstracts \#49}. (2017)
\item Bhure, S., {\bf Sankar, R.}, Hadland, N., Palotai, C. J., Le Beau, R. P., Koutas, N. Studies of Dark Spots and Their Companion Clouds on the Ice Giant Planets. {\it AAS/Division for Planetary Sciences Meeting Abstracts \#49}. (2017)
\item Palotai, C. J., {\bf Sankar, R.}, McCabe, T., Korycansky, D. Waves, Plumes and Bubbles from Jupiter Comet Impacts. {\it AAS/Division for Planetary Sciences Meeting Abstracts \#49}. (2017)
\item Flom, A., {\bf Sankar, R.}, Palotai, C. J., Dowling, T. E. Studying the Structure of Condensables Jupiter's 24deg Jet. {\it AAS/Division for Planetary Sciences Meeting Abstracts \#49}. (2017)
